\section{Changes to the Bifurcation Structure}
\label{sec:add.change}

\begin{enumerate}
	\item \begin{itemize}
		      \item ``type A'' parameter regions stop overlapping with the ``type A'' period regions above them (lower period, same number of points on branches $f_\B$ and $f_\D$)
		      \item Point where boundaries cross. On the left: no overlap, period-adding. On the right: overlap
		      \item This point moves right until no overlap exists anymore
	      \end{itemize}
	\item \begin{itemize}
		      \item ``type A'' parameter regions start overlapping with the ``type A'' period regions above right them (same period)
		      \item Point where boundaries cross. On the left: overlap. On the right: no overlap, ``type B'' parameter region
		      \item This point moves right, until no ``type B'' parameter region exists anymore
	      \end{itemize}
	\item \begin{itemize}
		      \item ``type A'' parameter regions stop overlapping with the ``type A'' parameter regions right to them (higher period, one more point on branches $f_\B$ and $f_\D$)
		      \item This seems to happen in an instant
	      \end{itemize}
\end{enumerate}

Timeline:
On the parameter line outlined above, the processes happen as follows.
First, the process (i) starts.
While it is happening, the process (ii) starts and finishes, before (i) finishes.
Lastly the process (iii) starts and finishes directly.
After all that, process (i) is the last to complete.

\input{Sections/70_Adding/21_disapp_b.tex}
\input{Sections/70_Adding/22_app_add.tex}
