\section{Standard Definitions}

The whole study of non-linear systems in discrete time is based on applying a model function iteratively.
We will ignore the continuous time case in this thesis.
In our case, the model function only has one dimension.
We say that our model is discontinuous, 1D, and discrete time.

\begin{definition}[Fixed Point]
	Let $x_{n+1} = f(x_n)$ be a 1D model in discrete time, where $f: \mathbb{R} \to \mathbb{R}$ is the model function. \\
	Then $x \in X$ is a fixed point, if $f(x) = x$.
\end{definition}

\begin{definition}[Iterate Function]
	Let $f: \mathbb{R} \to \mathbb{R}$ be a model function again.
	Then $f^k$ is the $k$-th iterate of this function, meaning that the function is applied $k$ times.
	Or defined recursively as $f^k(x) = f(f^{k-1}(x))$ and $f^1(x) = f(x)$.
\end{definition}

\begin{definition}[Cycle]
	Let $f: \mathbb{R} \to \mathbb{R}$ be a 1D, discrete time model function again.
	Then the sequence of $k$ points $\O_k = \{x_i | 0 \leq i < k\}$ is a $k$-cycle, if it satisfies the following conditions.
	\begin{align*}
		\forall 1 \leq i < k: \quad & f(x_i) = x_{i+1} \quad \land \quad f(x_{k-1}) = x_0
	\end{align*}
	If $x_0 \neq x_i$ for $1 \leq i < k$, then $k$ is the prime period of $\O_k$.
\end{definition}

For each point $x_i$ on a $k$-cylce $f^k(x_i) = x_i$.

\begin{definition}[Stability]
	Let $f: \mathbb{R} \to \mathbb{R}$ be a 1D, discrete time model function again.
	A fixed point $x^*$ is stable, if $|f'(x^*)| < 1$.
	Similarly, a $k$-cycle $\O_k = \{x_i | 0 \leq i < k\}$ is stable, if $|(f^k)'(x_i)| < 1$ for $0 \leq i < k$.
	Where $(f^k)'(x_i) = \prod_{j=0}^{k-1} f'(x_j)$.
\end{definition}

\begin{definition}[Bifurcation]
	A bifurcation is a qualitative change of the state space topology of a model under an infinitesimal small parameter variation.
\end{definition}
Meaning for example, that solutions to the model function or its iterate (fixed points and cycles) disappear or appear under a very small change to parameters.
The only bifurcations that will be important in this thesis are introduced in the next section.
That section will cover discontinuous models.
